### 2022-01-14 manuscript/manuscript.Rmd
Update manuscript.Rmd

---
title             : "A cross-disciplinary assessment of post-publication peer review policies and practice in influential scientific journals."
shorttitle        : "Post-publication peer review"

>>>>

---
title             : "A cross-disciplinary assessment of post-publication peer review policies and practice at influential scientific journals."
shorttitle        : "Post-publication peer review"
